Fractional Types

### 2019-11-23 fracGC/p.tex
more small things

\PIMEMstep{}
%% Note that step' uses step, but step is never shown
%% The need for the rewrite probably should be explained too.

The constructor for machine states takes a number which is the size of
the memory list. This size is maintained throughout the execution,
even if the intermediate types change. As a small example, the
following is a trace of the execution of \AgdaFunction{CNOT} applied
to 𝕋, 𝕋:
{\center\input{trace1.tex}}

@@

The main difference is that the state constructor does not take a
fixed size and indeed the size changes during execution as appropriate
to fit the elements of the type $A$. In particular, since fractional
values have a trivial representation, the cardinality of a fractional
type is 1, and hence $\eta$ used at type $A$ changes the size of the
memory list by the size of $A$. As an illustrative example,
Figure~\ref{fig:trace-id} shows a trace of the execution of \AgdaFunction{id'}
from Sec.~\ref{sub:id} applied to 𝕋:

>>>>

\PIMEMstep{}

%% Note that step' uses step, but step is never shown
%% The need for the rewrite probably should be explained too.

The constructor for machine states takes a number which is the size of
the memory list. This size is maintained throughout the execution,
even if the intermediate types change. As a small example, the
following is a trace of the execution of \AgdaFunction{CNOT} applied
to 𝕋, 𝕋:

{\center\input{trace1.tex}}

@@

The main difference is that the state constructor does not take a
fixed size and indeed the size changes during execution as appropriate
to fit the elements of the type $A$. In particular, since fractional
values have a trivial representation, the cardinality of a fractional
type is 1, and hence $\eta$ used at type $A$ grows the size of the
memory list by an $|A|$-factor. As an illustrative example,
we show a trace of the execution of \AgdaFunction{id'}
from Sec.~\ref{sub:id} applied to 𝕋:
